Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-10-29 Article/main.tex
Phil Added + Hippo Highlights

\subsection{Case Studies and the Similarities in Design Principles}
Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process. There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
\\\\
%---------------No. 1
The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}. 
\\\\
For the development of the artefact Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles. The first design principle followed is that the gamified system should make use of a \textit{story-based agent}\cite{Dincelli2020}. This means that a game should include some figure or character to guide users through the content as well as making use of story-telling in some capacity which is found to create curiosity within users\cite{Dincelli2020, Kapp2012a}. Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improves learning\cite{Dincelli2020}. The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}. 
\\\\
The findings of this case study was that making use of a gamified system that used either visual stimuli or text were better at relaying information that traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
\\\\
%---------------No. 2
The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}. 
\\\\
%---------------No. 3
The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}

@@

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Clear and Simple Goals  \\
Reflection	& Reflection			& Quality of Feedback and Rewards  \\
Feedback	& Conceptual-Procedural & Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
	-		& 		-				& Simplicity  \\
\hline

>>>>

\subsection{Case Studies and the Similarities in Design Principles}
Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process. There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
%---------------No. 1
The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}. 
For the development of the artefact Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles. The first design principle followed is that the gamified system should make use of a \textit{story-based agent}\cite{Dincelli2020}. This means that a game should include some figure or character to guide users through the content as well as making use of story-telling in some capacity which is found to create curiosity within users\cite{Dincelli2020, Kapp2012a}. Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improves learning\cite{Dincelli2020}. The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}. 
The findings of this case study was that making use of a gamified system that used either visual stimuli or text were better at relaying information that traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
%---------------No. 2
The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing and how to avoid becoming a victim to these attacks\cite{Sheng2007}. 
Sheng \textit{et al.}\cite{Sheng2007} made use of learning science theories in the games development and to refine the various iterations throughout the development process. The first two design principles discussed are \textit{reflection} and \textit{story-based agent encironment}\cite{Sheng2007}. These have already been mentioned  in the previous case study. Additionally, \textit{feedback} is also discussed in this study but specifically to how it was implemented. Anti-phishing Phil makes use of feedback both during, though displaying a short message for each choice during gameplay, and after a round of the game, through a score sheet and brief explanation of the links used\cite{Sheng2007}. 
The next design principle followed is the \textit{procedural-conceptual principle}\cite{Sheng2007}. It should be noted that Sheng \textit{et al.}\cite{Sheng2007} mention that procedural knowledge is also referred to as declarative knowledge. A similar definition to the one Kapp\cite{Kapp2012a} provides for procedural knowledge is given and as such the definition for declarative knowledge used in this study will be the one provided by Kapp\cite{Kapp2012a}. This principle states that these two knowledge domains, conceptual and procedural, hold a mutually supportive influence over the other\cite{Sheng2007}. In practice, and thus the development of a serious game, this means that learners should be given context to the processes they are being taught as without the context they may incorrectly apply processes\cite{Sheng2007}.
The findings of Anti-phishing phil showed that the serious game approach made users more knowledgeable on the topic and how to go about dealing with phishing\cite{Sheng2007}. While the game was a success for the most part, Sheng \textit{et al.}\cite{Sheng2007} mention that the game falls behind in one aspect - some users may become more susceptible to phishing as the game provided a fixed number of indicators to be aware of.
%---------------No. 3
The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teaching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}. One thing to be noted before discussing this case study is that it focused on the design and research needed for such a serious game and stated that future work could include the development and deployment of the game\cite{allers2021children}. Nonetheless, due to the level of planning done for the game as well as the positive outcome from an expert review process, this case study is still a viable option to consider.

@@

\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
\hline
Story-based	& Story-based 			& Simplicity  \\
Reflection	& Reflection			& Clear and Simple Goals  \\
Feedback	& Feedback 				& Quality of Feedback and Rewards  \\
	-		& Conceptual-Procedural	& Structure of the Challenge  \\
	-		& 		-				& Motion-based Interaction  \\
\hline
